SoK: The Evolution of Web Application Attack Defenses

### 2014-10-22 docs/questioning.tex
started describing defences

\title{SoK: Web Application Attack Defenses (in Question)}

@@

\section{Introduction}

@@

\section{Attacks}
\label{sec:attacks}

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.57]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:taxonomy}Attack model demonstrating web
application attacks that involve code injection ({\sc draft}).}
\end{figure*}

\section{Defenses for Detecting Web Application Attacks}

There are four main defensive approaches to counter
web application attacks, namely: {\it tainting},
{\it instruction set randomization} ({{\sc isr}}),
{\it policy enforcement} and {\it training}.

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.57]{defenses.pdf}
\end{center}
\caption{\label{fig:taxonomy}The basic categories of web application
attack countermeasures ({\sc draft}).}
\end{figure*}

>>>>

\title{SoK: The Evolution of Web Application Attack Defenses}

@@

\section{Introduction Remarks}

@@

\section{Attacks and Background}
\label{sec:attacks}

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.57]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks that involve code injection ({\sc draft}).}
\end{figure*}

\section{Web Application Attacks Defenses}
\label{sec:defs}

Figure~\ref{fig:defenses} presents a taxonomy of the
approaches that counter web application attacks based on
code injection vulnerabilities.
We can identify two main approaches, namely:
{\it protection} and {\it detection}.
The former involves mechanisms that make applications
immune to different attack vectors by design~\cite{JL75,L81}.
The latter incorporates a variety of methods and
schemes that inspect the behavior of applications
and detect attacks based on specific criteria~\cite{D76,A00}.

\subsection{Protection}
\label{sec:prot}

Here we analyze the three different protection approaches.

\subsubsection{Parse-Tree Validation}

\subsubsection{Securing Mashups}

\subsubsection{Instruction Set Randomization --- ISR}

{\sc isr} is a method that contrary to the previous
two approaches, has been applied to counter
different kinds of application attacks~\cite{K09b,KKP03}.

\subsection{Detection}

% {\it tainting},
% {\it instruction set randomization} ({{\sc isr}}),
% {\it policy enforcement} and {\it training}.

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.57]{defenses.pdf}
\end{center}
\caption{\label{fig:defenses}The basic categories of web application
attack countermeasures ({\sc draft}).}
\end{figure*}
